Estimating Output Loss due to being Unrecognized as States

### 2019-03-08 paper/paper.tex
Minor revision for the data description section #40

\paragraph{Transnistria and Moldova} 
The boundaries of Transnistria and Moldova proper come from the first-level administrative boundary data from GADM (2018). 
The actual territory of Transnistria, however, differs from the official boundary between Transnistria and the rest of Moldova. 
Transnistria occupies some small parts of Moldova proper while Moldova controls some small parts of Transnistria (Tchepalyga\ 1997, p.\ 31). 
However, the spatial data on the exact boundary between the two is unavailable. 
Consequently, we use the official boundary as an approximation.

\paragraph{Abkhazia, South Ossetia and Georgia proper}  
The spatial data on the boundaries of Abkhazia, South Ossetia, and Georgia proper is obtained from ACASIAN (2014). 
This dataset was created in conjunction with the Institute of Geography at Russian Academy of Sciences, with the official map definitive as of the 1989 Soviet Census.

>>>>

\paragraph{Transnistria and Moldova proper} 
The boundaries of Transnistria and Moldova proper come from the first-level administrative boundary data from GADM (2018). 
The actual territory of Transnistria, however, differs from the official boundary between Transnistria and the rest of Moldova. 
Transnistria occupies some small parts of Moldova proper while Moldova controls some small parts of Transnistria (Tchepalyga\ 1997, p.\ 31). 
However, the spatial data on the exact boundary between the two is unavailable. 
Consequently, we use the official boundary as an approximation.

\paragraph{Abkhazia, South Ossetia and Georgia proper}  
The spatial data on the boundaries of Abkhazia, South Ossetia, and Georgia proper is obtained from ACASIAN (2014).%
\footnote{
	We do not use GADM (2018) because South Ossetia does not exist in the official subdivisions of Georgia.
	} 
This dataset was created in conjunction with the Institute of Geography at Russian Academy of Sciences, with the official map definitive as of the 1989 Soviet Census.
